Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-22 R0V0.tex
Change the notation of the sets C and add the set proj

\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-2y_i\;,\\
 \underline{Y}_{ij}(q)=&-2-2\sum_{k=1}^4 y_k^2+x_k^2\;.
\end{align*}

>>>>

\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $i\in\mathbb{N}_{[1,4]}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\mathbb{R}^8$, $\mathbf{C}(i)=\mathbb{R}^8$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-2y_i\;,\\
 \underline{Y}_{ij}(q)=&-2-2\sum_{k=1}^4 y_k^2+x_k^2\;.
\end{align*}
